### 2020-01-24 probabilisticProgrammingMartingales.tex
Some thoughts on extension to score, and a.e. termination

\definecolor{oxblue}{RGB}{0,33,71}
\definecolor{oxgold}{HTML}{a0630a}
\usepackage[final,
bookmarks,
bookmarksopen,
colorlinks,
final,
linkcolor=oxred,
citecolor=oxgold,
pdfstartview=FitH ]{hyperref}
%%
%% END {Luke's Macros}

@@

\lo{\LaTeX. For references, I recommend using the package {\tt natbib} with {\tt apalike} bibliography style (author-year is more reader-friendly), and placing the references in a separate {\tt .bib} file.
I simply copy-and-paste the bib data from DBLP e.g.~\url{https://dblp.uni-trier.de/pers/hd/o/Ong:C==H=_Luke}.}

@@

\lo{\textbf{Further directions}

\smallskip

>>>>

\definecolor{oxblue}{RGB}{0,33,71}
\definecolor{oxgold}{HTML}{a0630a}
\usepackage[final,
bookmarks,
bookmarksopen,
colorlinks,
final,
linkcolor=red,
citecolor=oxgold,
pdfstartview=FitH ]{hyperref}
%%
%% END {Luke's Macros}

@@

\lo{23 Jan:

\paragraph{Some thoughts about extension to $\mathsf{score}$}

- I still think that the operational semantics (reduction semantics) of SPCF (i.e.~with $\mathsf{score}$) is not problematic. However the notion of a.e.~termination is interesting and would benefit from further thought.

- I would propose that you use the language SPCF defined in \citep{MakOP20b}. They use a big-step reduction semantics. I would sugget that, by contrast, you develop a small-step reduction semantics for it (by a mild adaptation of your $\red : \Lambda \times S \to \Lambda \times S$).

- You will find that your example 
\[
f \, n = n \oplus_{\frac{1}{2}} (\mathsf{score} \, 3 \, ; \, f \, (n+1))
\]
is not definable in SPCF, but a variant (in which the branching probabilities are drawn from the entropy sequence) is. OK, we will need to assume that their $\mathbb{S} := \mathbb{R}^\omega$ is replaced by your $S$.

- Consider the notion of a.e.~termination defined in \citep{MakOP20b}\footnote{\url{https://drive.google.com/open?id=1JzxV0lCkZu4d7szQOzkcKspqqo8u2BP0}} (towards the end of \S 3): a program $s$ is a.e.~terminating if the set of entropy sequences where $s$ does not evaluate to a value has measure zero.
The intuition is that scoring is about model building, and does not by itself ``affect termination''.
}

\bigskip

\lo{22 Jan:
\LaTeX. For references, I recommend using the package {\tt natbib} with {\tt apalike} bibliography style (author-year is more reader-friendly), and placing the references in a separate {\tt .bib} file.
I simply copy-and-paste the bib data from DBLP e.g.~\url{https://dblp.uni-trier.de/pers/hd/o/Ong:C==H=_Luke}.}

@@

\lo{22 Jan: 
\paragraph{Further directions}
